\documentclass[10pt,a4paper]{article}

% --------------------
% Packages
% --------------------
\usepackage[left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}

% --------------------
% Formatting
% --------------------
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0pt}
  {}
  [\titlerule]

\renewcommand{\labelitemi}{--}

% --------------------
% Document
% --------------------
\begin{document}

% --------------------
% Header
% --------------------
\begin{center}
    {\LARGE \textbf{Sagar Gupta}} \\[4pt]
    \href{mailto:sg36.sagargupta26@gmail.com}{sg36.sagargupta26@gmail.com}\texttt{ | }+91-7872827780\texttt{ | }\href{https://linkedin.com/in/sagar-gupta-02091783}{linkedin.com/in/sagar-gupta-02091783}
\end{center}

% --------------------
% Summary
% --------------------
\section*{Professional Summary}
 Backend Engineer with 6+ years of experience designing and building secure, scalable, high-availability backend systems using Java, Spring Boot, REST APIs, Microservices, and AWS. Experienced in authentication platforms, cloud migration, CI/CD modernization, and system modernization within regulated banking environments.

% --------------------
% Skills
% --------------------
\section*{Technical Skills}
\textbf{Languages:} Java 8, Java 17, JS(basic), Python(basic) \\
\textbf{Frameworks and Technologies:} Spring, Spring Boot, REST APIs, React \\
\textbf{Architecture:} Microservices, Cloud Native Architecture, Secure Authentication Systems, High Availability Systems \\
\textbf{Databases:} SQL (MySQL)\\
\textbf{Cloud \& DevOps:} AWS, CI/CD, Git, GitLab CI, Jenkins, Docker(basic) \\
\textbf{Engineering Practices:} System Modernization, Cloud Migration, Mutation Testing, Technical Debt Reduction

% --------------------
% Experience
% --------------------
\section*{Professional Experience}

\textbf{Barclays} \hfill Pune \\
\textit{Backend Engineer} \hfill Jul 2019 -- Present
\begin{itemize}[leftmargin=*]
    \item Delivered app-based 2FA for Barclays Online Banking, replacing legacy PINsentry hardware. Improved authentication speed and user experience via push-based real-time approvals, delivering ~£6M savings over 5 years.
    \item Led CI/CD modernization by migrating build and deployment pipelines from Jenkins to GitLab CI, introducing automated quality, security, and compliance gates that improved release stability and developer productivity.
    \item Led modernization of legacy Java and Spring Boot services, improving application performance by 50\% (3s-1.5s) while maintaining backward compatibility and supporting scalable microservices adoption.
    \item Implemented mutation testing using PIT (Java) and Stryker (React), strengthening test effectiveness and improving defect detection across backend and frontend applications.
    \item Created a separate journey to support accessibility and vulnerability requirements, enabling customers to receive bank statements in Braille, large print, and audio formats.
    \item Implemented a “Go Paperless” interstitial page prompting customers to switch from paper statements to digital delivery, reducing paper costs by ~£200K/year.
    \item Led cloud migration of authentication microservices to AWS, implementing cloud-native stateless services that improved scalability, high availability, and deployment reliability.
    \item Enabled reuse of an existing React application by exposing stable, backward-compatible backend APIs and integrating them into a mobile WebView flow.
\end{itemize}

\vspace{4pt}

\textbf{TCG Digital} \hfill Kolkata \\
\textit{Mobile Developer Intern} \hfill Mar 2018 -- May 2018
\begin{itemize}[leftmargin=*]
    \item Developed a mobile application using React Native to visualize import-export data across major Indian ports.
\end{itemize}


% --------------------
% Projects
% --------------------
\section*{Academic \& Personal Projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{New Product Sales Forecasting (Masters Project):} Implemented data pipelines and analytical models in Python to forecast product sales by combining historical data with sentiment analysis.
    \item \textbf{URL Shortener with Analytics:} Built a URL shortener with analytics using Spring Boot, Redis, and MySQL. Designed caching and lookup strategies achieving sub-50ms redirect latency and deployed on AWS EC2 with CloudWatch monitoring.
\end{itemize}


% --------------------
% Education
% --------------------
\section*{Education}
\textbf{Indian Institute of Technology, Kharagpur}  \\
Dual Degree (B.Tech + M.Tech), Industrial Engineering \hfill 2014 -- 2019 \\
CGPA: 7.39/10

\end{document}
